TRIK Studio: Technical Introduction

### 2017-02-06 2017-trikStudioEnglish/trikStudioEnglish.tex
Added text about Stepik checker

В режиме двумерной симуляции доступна возможность автоматической проверки задач (см. раздел~\ref{chapter:constraintsChecker}). Программа проверки пишется на внутреннем событийном текстовом языке, файл с сохранением модели симулируемого мира и программы проверки затем может распространяться как задача для учеников. На основе этой системы был запущен курс дистанционного обучения на платформе Stepic\footnote{https://stepic.org/s/7qe3xj4Z  (дата обращения: 14.05.2016)} с видео-лекциями по основам кибернетики, робототехники и использованию среды TRIK Studio, множеством небольших тестов и 20 задачами образовательной робототехники. Каждая задача может быть скачана, решена и проверена в TRIK Studio на локальном компьютере и сдана на сервер, где система проверки запустит решение на своих тестах (подобно формату решения задач на соревнованиях ACM ICPC).

@@

>>>>

В режиме двумерной симуляции доступна возможность автоматической проверки задач (см. раздел~\ref{chapter:constraintsChecker}). Программа проверки пишется на внутреннем событийном текстовом языке, файл с сохранением модели симулируемого мира и программы проверки затем может распространяться как задача для учеников. На основе этой системы был запущен курс дистанционного обучения на платформе Stepik\footnote{https://stepik.org/s/7qe3xj4Z  (дата обращения: 14.05.2016)} с видео-лекциями по основам кибернетики, робототехники и использованию среды TRIK Studio, множеством небольших тестов и 20 задачами образовательной робототехники. Каждая задача может быть скачана, решена и проверена в TRIK Studio на локальном компьютере и сдана на сервер, где система проверки запустит решение на своих тестах (подобно формату решения задач на соревнованиях ACM ICPC).

@@

This functionality is also used as an automatic checker of exercises for MOOC on Stepik platform\footnote{https://stepik.org/s/7qe3xj4Z}. Without such checker it would be impossible to provide feedback to possibly large number of students, making course much less interactive. From a technical point of view checker is a set of scripts which launch "`headless"' interpreter (i.e. interpreter without GUI) on a correct field with correct constraints. Checker is hooked up into Stepik infrastructure and runs in a separate Docker\footnote{https://www.docker.com/} container when new solution is submitted. Checker has several fields and corresponding constraint descriptions for each task (from one to five), each solution is checked against all those fields to test that it works in different situations and is not hardcoded. Fields are hidden from the user but error reporter output does gets displayed, so students can guess what went wrong (well, theoretically. But it's better than traditional ACM ICPC system, where only a number of incorrect test and a general type of error are reported).

Checker can also send a visual representation of a field with a trace of a robot to a client. Trace consists of points of a robot trajectory and values reported by its sensors, and this trace can be played back by a web application described in~\cite{zakharov2016web} (in Russian). This web application also allows to actually create solutions for almost all tasks from the course right in the browser, form a correct TRIK Studio save file and run it on a server on checker, playing back the result, so a student perceives this as "`TRIK Studio in a browser"'. This application works standalone, but is not integrated into Stepik course yet due to technical difficulties related to Stepik infrastructure.
